---
output: html_document
editor_options: 
  chunk_output_type: console
---

#### Infographic

For the Infographic, make sure there is a link to https://unity.nl/themas/slapen

(Maybe also in the animation?)

##### Sleeping behavior

```{r infographic-sleeping-behavior-categorization}

sleepHours_toCategory <- function(x) {
  return(
    factor(
      ifelse(is.na(x),
             NA,
             ifelse(x < 3,
                    1,
                    ifelse(x < 6,
                           2,
                           ifelse(x < 8,
                                  3,
                                  4)))),
      levels=1:4,
      labels=c("Minder dan 3 uur",
               "4-5 uur",
               "6-7 uur",
               "8 uur of meer"))
  );
}

###-----------------------------------------------------------------------------
### Sleep quantity categorization
###-----------------------------------------------------------------------------

dat$weekdaySleep_cat <-
  sleepHours_toCategory(dat$weekdaySleep);

dat$goingOutSleep_cat <-
  sleepHours_toCategory(dat$goingOutSleep);

dat$atFestivalSleep_other_cat <-
  sleepHours_toCategory(dat$atFestivalSleep_other);

dat$afterFestivalSleep_other_cat <-
  sleepHours_toCategory(dat$afterFestivalSleep_other);

```

###### Hours of sleep on a weekday:

```{r infographic-sleeping-behavior-1}
pander::pander(rosetta::freq(dat$weekdaySleep_cat));
```

###### Hours of sleep when going out:

```{r infographic-sleeping-behavior-2}
pander::pander(rosetta::freq(dat$goingOutSleep_cat));
```

###### Hours of sleep at a multi-day festival:

```{r infographic-sleeping-behavior-3}
pander::pander(rosetta::freq(dat$atFestivalSleep_other_cat));
```

###### Hours of sleep on after a one-day festival:

```{r infographic-sleeping-behavior-4}
pander::pander(rosetta::freq(dat$afterFestivalSleep_other_cat));
```

##### Perceived sleeping quality and ease

```{r infographic-sleeping-quality-and-ease, results='asis'}

###-----------------------------------------------------------------------------
### Sleep quality
###-----------------------------------------------------------------------------

sleepQualityVarsRaw <-
  grep('SleepBeliefs_att', names(dat), value=TRUE);

sleepQualityLabs <-
  labelDf$subQuestion[labelDf$varNames.cln %in% grep('SleepBeliefs_att',
                                                     names(dat),
                                                     value=TRUE)];

sleepQualityLabs <-
  gsub("\\n", " ", sleepQualityLabs);

sleepQualityVarsCat <-
  paste0(sleepQualityVarsRaw, "_cat");

dat[, sleepQualityVarsCat] <-
  lapply(dat[, sleepQualityVarsRaw],
         function(x) {
           return(ifelse(is.na(x),
                         NA,
                         ifelse(x < 4,
                                1,
                                ifelse(x == 4,
                                       2,
                                       3))));
         });

substanceSleepQualityCategories_barplot <-
  ufs::ggEasyBar(dat,
                 rev(sleepQualityVarsCat),
                 labels = rev(sleepQualityLabs),
                 sortByMean = FALSE) +
    ggplot2::theme(legend.position="none",
                   text = ggplot2::element_text(family="Titillium Web"),
                   axis.text.x = ggplot2::element_blank(),
                   panel.grid = ggplot2::element_blank(),
                   axis.ticks = ggplot2::element_blank());

cat("\n\n\n\n");

suppressWarnings(
  ufs::knitAndSave(substanceSleepQualityCategories_barplot,
                   path = workingPath,
                   figWidth = 7, figHeight = 4,
                   "Bar plot of perceived sleep quality after taking different substances"));

cat("\n\n\n\n");

sleepQualityVarsCatFreqs <-
  ufs::multiVarFreq(dat,
                    sleepQualityVarsCat,
                    labels = sleepQualityLabs,
                    sortByMean = FALSE);
colnames(sleepQualityVarsCatFreqs) <-
  c("Slechter", "Zelfde", "Beter");

knitr::kable(
  round(100 * sleepQualityVarsCatFreqs /
          rowSums(sleepQualityVarsCatFreqs))
);

cat("\n\n\n\n");

###-----------------------------------------------------------------------------
### Sleep ease
###-----------------------------------------------------------------------------

sleepEaseVarsRaw <-
  grep('SleepBeliefs_pbc', names(dat), value=TRUE);

sleepEaseLabs <-
  labelDf$subQuestion[labelDf$varNames.cln %in% sleepEaseVarsRaw];

sleepEaseLabs <-
  gsub("\\n", " ", sleepEaseLabs);

sleepEaseVarsCat <-
  paste0(sleepEaseVarsRaw, "_cat");

dat[, sleepEaseVarsCat] <-
  lapply(dat[, sleepEaseVarsRaw],
         function(x) {
           return(ifelse(is.na(x),
                         NA,
                         ifelse(x < 4,
                                1,
                                ifelse(x == 4,
                                       2,
                                       3))));
         });

substanceSleepEaseCategories_barplot <-
  ufs::ggEasyBar(dat,
                 rev(sleepEaseVarsCat),
                 labels = rev(sleepEaseLabs),
                 sortByMean = FALSE) +
    ggplot2::theme(legend.position="none",
                   text = ggplot2::element_text(family="Titillium Web"),
                   axis.text.x = ggplot2::element_blank(),
                   panel.grid = ggplot2::element_blank(),
                   axis.ticks = ggplot2::element_blank());

cat("\n\n\n\n");

suppressWarnings(
  ufs::knitAndSave(substanceSleepEaseCategories_barplot,
                   path = workingPath,
                   figWidth = 7, figHeight = 4,
                   "Bar plot of perceived sleep ease after taking different substances"));

cat("\n\n\n\n");

sleepEaseVarsCatFreqs <-
  ufs::multiVarFreq(dat,
                    sleepEaseVarsCat,
                    labels = sleepEaseLabs,
                    sortByMean = FALSE);
colnames(sleepEaseVarsCatFreqs) <-
  c("Slechter", "Zelfde", "Beter");

cat("\n\n\n\n");

knitr::kable(
  round(100 * sleepEaseVarsCatFreqs /
          rowSums(sleepEaseVarsCatFreqs))
);

cat("\n\n\n\n");

```

##### Perceived norms regarding sleep

All perceived norms are overwhelmingly positive.

```{r infographic-sleeping-norms, results='asis'}

injunctiveNormVarsRaw <-
  grep("NrmInjunct_[^_]+$", names(dat), value=TRUE);
descriptiveNormVarsRaw <-
  grep("NrmDescr_[^_]+$", names(dat), value=TRUE);

injunctiveNormLabs <-
  paste0(gsub("_.*", ": ", injunctiveNormVarsRaw),
         labelDf$subQuestion[labelDf$varNames.cln %in% injunctiveNormVarsRaw]);
descriptiveNormLabs <-
  paste0(gsub("_.*", ": ", descriptiveNormVarsRaw),
         labelDf$subQuestion[labelDf$varNames.cln %in% descriptiveNormVarsRaw]);

injunctiveNormLabs <-
  gsub("\\n", " ", injunctiveNormLabs);
descriptiveNormLabs <-
  gsub("\\n", " ", descriptiveNormLabs);

injunctiveNormVarsCat <-
  paste0(injunctiveNormVarsRaw, "_cat");
descriptiveNormVarsCat <-
  paste0(descriptiveNormVarsRaw, "_cat");

dat[, injunctiveNormVarsCat] <-
  lapply(dat[, injunctiveNormVarsRaw],
         function(x) {
           return(ifelse(is.na(x),
                         NA,
                         ifelse(x < 4,
                                1,
                                ifelse(x == 4,
                                       2,
                                       3))));
         });
dat[, descriptiveNormVarsCat] <-
  lapply(dat[, descriptiveNormVarsRaw],
         function(x) {
           return(ifelse(is.na(x),
                         NA,
                         ifelse(x < 3,
                                1,
                                ifelse(x < 6,
                                       2,
                                       3))));
         });

injunctiveNormFreqs <-
  ufs::multiVarFreq(dat,
                    injunctiveNormVarsCat,
                    labels = injunctiveNormLabs,
                    sortByMean = FALSE);
colnames(injunctiveNormFreqs) <-
  c("Afkeurend", "Neutraal", "Goedkeurend");

cat("\n\n\n\n");

knitr::kable(
  round(100 * injunctiveNormFreqs /
          rowSums(injunctiveNormFreqs))
);

cat("\n\n\n\n");

descriptiveNormFreqs <-
  ufs::multiVarFreq(dat,
                    descriptiveNormVarsCat,
                    labels = descriptiveNormLabs,
                    sortByMean = FALSE);
colnames(descriptiveNormFreqs) <-
  c("(Bijna) nooit", "Soms tot vaak", "(Bijna) altijd");

cat("\n\n\n\n");

knitr::kable(
  round(100 * descriptiveNormFreqs /
          rowSums(descriptiveNormFreqs))
);

cat("\n\n\n\n");

```

##### Animation

Punten voor het animatiefilmpje:

- Het blijkt dat bijna iedereen aangeeft dat er een positieve norm is met betrekking tot voldoende slapen.
- Het blijkt ook dat het de meeste mensen niet uitmaakt wat anderen vinden; dus die norm is niet noodzakelijk de effectiefste route in interventies. Echter, de norm zelf (eerste bullet) hing wel samen met attitude en intentie, dus deze nuancering misschien weglaten?
- Mensen die meer last hebben van slaapgebrek (concentratieproblemen) hebben een betere slaaphygiene.
- "FOMO", de angst dingen te missen door te gaan slapen, lijkt geen rol te spelen op basis van de Party Panel data.
- Belangrijk opvattingen met betrekking tot van-te-voren voldoende slaap krijgen lijken:
    - De verwachting dat van-te-voren voldoende slaap krijgen, slaapgebrek door uitgaan op kan vangen.
    - De verwachting dat je meer kunt genieten van het uitgaan als je van-te-voren voldoende slaapt.
- Belangrijk opvattingen met betrekking tot na het uitgaan bijslapen lijken:
    - Als mensen het frustrerend vinden om in bed te liggen als ze niet goed kunnen slapen, is de kans dat de goed bijslapen na het uitgaan iets lager.
- Slaapgewoonte is grotendeels een gewoontegedrag. Interventies zouden zich dus moeten richten op methoden voor gewoonteverandering. 

###### How often do participants make sure they sleep enough?

```{r animation-sleeping-hygiene-1}

enforceSleepPattern_to_cat <- function(x) {
  return(
    factor(
      ifelse(is.na(x),
             NA,
             ifelse(x < 3,
                    1,
                    ifelse(x == 3,
                           2,
                           3))),
      levels=1:3,
      labels=c("Soms",
               "Wel eens",
               "Vaak"))
  );
}

dat$sleepBehav_pre_cat <-
  enforceSleepPattern_to_cat(dat$sleepBehav_pre);
dat$sleepBehav_post_cat <-
  enforceSleepPattern_to_cat(dat$sleepBehav_post);

```

Scale from '(almost) never', 'sometimes', 'regularly', 'often', '(almost) always'.

####### 3 nights before going out

```{r infographic-sleep-behavior-1}

pander::pander(rosetta::freq(dat$sleepBehav_pre_cat));

```

####### 3 nights after going out

```{r infographic-sleep-behavior-2}

pander::pander(rosetta::freq(dat$sleepBehav_post_cat));

```


