---
title: "Party Panel 19.1-pre2 Report"
author: "Lizet Wilkens, Judith Noijen & Gjalt-Jorn Peters"
date: "`r format(Sys.time(), '%d %b %Y at %H:%M:%S');`"
output:
  html_document:
    toc: true
    #toc_float: true
    toc_depth: 5
    theme: united
editor_options: 
  chunk_output_type: console
---

Party Panel 19.1-pre2 Report
============================

Introduction
------------

Party Panel is a Dutch panel study where determinants and beliefs underlying health behaviors in the Dutch nightlife are mapped. The fifth (2019) wave explored determinants of behavior related to sleeping hygiene.

This document is the report of the second pre-study, where members of the target population responded to a number of open questions, comparable to a belief elicitation procedure as recommended by Fishbein & Ajzen (2010). Put simply, they were asked about what they thought were the reasons people did, or did not, engage in the target behaviors selected in the first round.

```{r echo=FALSE, warning=FALSE, message=FALSE }

########################################################################
### Basic configuration variables; normally all you have to change
########################################################################

### Set basic configuration variables
if (!exists('ppWave')) ppWave <- '19.1';
if (!exists('ppReport')) ppReport <- 'pre2';

########################################################################
### Packages
########################################################################

ufs::safeRequire('here');
ufs::safeRequire('knitr');
ufs::safeRequire('pander');
ufs::safeRequire('xtable');

### Get dev versions of some packages
remotes::install_gitlab("r-packages/ufs",
                        upgrade="never",
                        quiet=TRUE);
remotes::install_gitlab("r-packages/yum",
                        upgrade="never",
                        quiet=TRUE);
remotes::install_gitlab("r-packages/rock",
                        upgrade="never",
                        quiet=TRUE);

########################################################################
### Settings
########################################################################

knitr::opts_chunk$set(echo=FALSE);
knitr::opts_chunk$set(cache=FALSE);
knitr::opts_chunk$set(comment=NA);

options(width = 160);
options(xtable.type = "html");
pander::panderOptions('knitr.auto.asis', FALSE);
pander::panderOptions('table.split.table', Inf);

########################################################################
### Set the variables with the paths
########################################################################

### Set the additional paths
outputPath <- here::here('preparation', 'pre2', 'output');
workingPath <- here::here('preparation', 'pre2', 'output');
dataPath <- here::here('preparation', 'pre2', 'data--[[PUBLIC]]');
scriptPath <- here::here('preparation', 'pre2', 'scripts');

########################################################################
### Objects to store data for potential later use
########################################################################

### Make object(s) for Party Panel data
if (!exists('ppDat')) ppDat <- list();
if (!(ppWave %in% names(ppDat))) ppDat[[ppWave]] <- list();
ppDat[[ppWave]][[ppReport]] <- list();

```


```{r, results='asis', fig.height=22}

### Pass customized 'codes' to only extract DCT specifications
parsedSources <-
  rock::parse_sources(dataPath,
                      codeRegexes = c(codes = "\\[\\[dct\\:([a-zA-Z0-9._>-]+)\\]\\]"),
                      persistentIds=c("caseId"));

### Store merged code dataframe
write.csv(parsedSources$mergedSourceDf,
          file.path(outputPath,
                    "mergedSourceDf.csv"),
          row.names=FALSE);

### Write & show results
cat(rock::collect_coded_fragments(parsedSources,
                                  output=file.path(outputPath,
                                                   "coded-fragments.md")));

```

